BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2016-01-13 Paper/BOAST.tex
Added reference to Heterogeneous Programming Library (HPL).

>>>>

  Heterogeneous Programming Library~\cite{vinas2013exploiting} (HPL) is maybe
the most similar to BOAST. It is an autotuning kernel library in C++ that targets
OpenCL. It uses an EDSL in C++ to describe generic computing kernels. Like when
using BOAST, optimization are left to the users and written directly using the
EDSL. The syntax is very close to real C++ with the classical control
structures having a trailing underscore. But whereas BOAST re-interprets the
same code while changing the environment, in HPL each expression is stored in a
tree and the tree is reevaluated in a different environment.
